---
title: "OldFaithfulGeyser"
author: "Jeff Sternin"
date: "March 15, 2018"
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 1. Summary

We provide interactive Shiny application based on data collected on YeallowStone Park Old Faithful Gyser.  
[Old Faithful Geyser](http://www.wildnatureimages.com/Old-Faithful-Geyser-Photos.htm)  

This application show histograms of waiting time to next eruption, eruptions duration.    
Also allows to investigate relationship between eruption time and waiting time until next eruption.    
Here's the link to shiny app.    
[Old Faithful Geyser App](https://devdataproducts.shinyapps.io/DevDataProducts/)  
This application shows 3 interactive tabs:  
1. Waiting time histogram  
2. Eruption time histogram   
3. Linear regression between eruptions time and waiting time to next eruption,  
based on user selection of data points  
[github repository](https://github.com/jsternin/OldFaithfulGeyser)

## 2. Tab panels: Histograms - Waiting time, Eruptions time   

Waiting time histogram shows distribution of wait time until   
next eruptions. User can control number of bins in histogram   
using first slider. First slider name "Waiting (min)" controls  
number of bins in historgram. Make sure that First tab panel   
("Waiting (min) Histogram") is selected. Default number of   
bins is 30. Waiting time is between 50 and 90 min.  
Eruptions time histogram shows distribution of Eruptions time.      
User can control number of bins in histogram using   
second slider. Second slider name "Eruptions (min)" controls  
number of bins in historgram. Make sure that Second tab panel  
("Eruptions (min) Histogram") is selected. 
Eruptions time is between 1.5 and 5 min.  

## 3. Tab panel: Eruptions~waiting regression

Tab Eruptions-waiting time shows points in coordinates   
X-eruption time, Y- waiting time until next eruption.  
User can select (swipe) any subset of points and   
regression line will be interactively built showing    
Slope, Intersect and Ajusted Sum of Squares.  
Ajusted sum of suares is $adjSumSq = 1-RSS/TSS$  
where $RSS = sum((data - fitted)^{2}$ 
$TSS = sum((data - mean(data)^{2})$   
Ajusted sum of suares shows percentage of data     
that model explains. Next slide shows regression  
line when all points are selected.

***

```{r pressure}
plot(faithful$eruptions, faithful$waiting,  xlab = "eruptions (min)",
         ylab = "waiting (min)", main = "Old Faithful Geyser",
         cex = 1.5, pch = 16, bty = "n")
fit <- lm(waiting~ eruptions, data=faithful)
abline(fit, col = "blue", lwd = 2)
print(sprintf("Slope: %4.2f Intercept:%4.2f Adj R squared: :%4.3f  ",
              fit[[1]][2],fit[[1]][1],summary(fit)[[9]]))
```

